---
title: "Data cleaning for RedCap measures"
author: "Meriah DeJoseph"
date: "Summer 2022"
output: html_document 
---

## About
This script creates clean child and parent measures.

## Libraries
```{r libraries, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(dplyr)
library(e1071)
library(readr)
library(Hmisc)
library(corrplot)
library(sjstats)
library(ppcor)
library(arsenal)
```

## Create child and parent raw merged files
```{r load_data, warning=FALSE, include=TRUE, cache=TRUE, message=FALSE}

#Set wd to where the data is
setwd("~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/RedCap merging and cleaning") 

#read in entire redcap file
df_raw <- read_csv("LearningInEarlyAdole_DATA_2022-08-03_1711_2.csv")

#save out the raw child file
df_child_raw <- df_raw %>% 
  filter(poc == 2) %>% #select only child responses (2)
  dplyr::select(id, poc, c(pds_9:freeresponse_2))

#merge child age from masterlist
child_age_var <- read_csv("LEAP child age var.csv")
as.character(child_age_var$id)
as.character(df_child_raw$id)
df_child_raw <- inner_join(child_age_var, df_child_raw, by = 'id')  

#write.csv(df_child_raw,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/RedCap merging and cleaning/df_child_raw.csv")

#save out the raw parent file
df_parent_raw <- df_raw %>% 
  filter(poc == 1) %>% #select only parent responses (1)
  dplyr::select(id, poc, c(csex:free_response))

#write.csv(df_parent_raw,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/RedCap merging and cleaning/df_parent_raw.csv")

```

## Create a cleaned demo dataset
```{r load_data, warning=FALSE, include=TRUE, cache=TRUE, message=FALSE}

#create and write raw demo dataset
rawDemo <- df_parent_raw %>% 
  dplyr::select(id, poc, c(csex:rcvmedic))

#merge child age
rawDemo <- inner_join(child_age_var, rawDemo, by = 'id')  

#write.csv(rawDemo,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/RedCap merging and cleaning/demo_raw.csv")
  
#recode vars I will need for analyses and label as "demo_clean"
#clean & save out: child sex, age, race, highest parent ed, income, INR, grades, 
#relation to kid, free lunches, partnered, number moves

#dummy code child sex and race
demo <- rawDemo %>% 
  mutate(female = csex,
         white = cident___5,
         hispanic = chispanic,
         asian = cident___2,
         other = cident___6
         )
  
#get highest parent ed
demo <- demo %>% 
  mutate(highed = ifelse(momed>daded, momed, daded))

#create INR variable 
#uses this guide: 
#https://www.projusticemn.org/fedpovertyguidelines/

demo <- demo %>% 
  dplyr::mutate(INR = ifelse(pplhouse==2, (totincome/18310), 
               ifelse(pplhouse==3, (totincome/23030),
               ifelse(pplhouse==4, (totincome/27750),
               ifelse(pplhouse==5, (totincome/32470),
               ifelse(pplhouse==6, (totincome/37190),
               ifelse(pplhouse==7, (totincome/41910),
               ifelse(pplhouse==8, (totincome/46630),
               ifelse(pplhouse==9, (totincome/51350), NA)))))))))

#recode free lunch variable to dummy (here 0 = yes)
demo <- demo %>% 
  dplyr::mutate(freelunch = ifelse(rcvschfd==0, 1, 0))

#select out necc vars for demo dataset
demo_clean <- demo %>% 
  dplyr::select(id, poc, cage, female, white, hispanic, asian, other,
         highed, INR, freelunch, totincome, nummoves, cgrades, 
         rpartner, rrelation)
  
write.csv(demo_clean,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/RedCap merging and cleaning/demo_clean.csv")

```

## Create individual parent-reported measures and aggregate scores
```{r load_data, warning=FALSE, include=TRUE, cache=TRUE, message=FALSE}


```

## Create individual child-reported measures and aggregate scores
```{r load_data, warning=FALSE, include=TRUE, cache=TRUE, message=FALSE}


```













## Pull out neccessary variables for analyses & mutate vars
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

#pull out all vars I think I'll need for analyses
df_bothV <- df_merged_raw %>% 
  dplyr::select(Subject, Order, 
                Block, Ecological, LineDrawing, 
         OrderList, OrderList.Cycle, OrderList.Sample, 
         Picture1, Picture2, Picture3, Picture4, Picture5, Picture6,
         Picture7, Picture8, Picture9, Picture10, Picture11, Picture12,
         Procedure.Block., 
         Running.Block., Trial, 
         Acq100Blk, Acq100Blk.Cycle, Acq100Blk.Sample, Condition,
         CorKeyAns, CorrectAnswer, Message,
         ReversalBlk, ReversalBlk.Cycle, ReversalBlk.Sample,
         Stim, 
        trial_type, Active, Version, Total, Stm.RESP) %>% 
 filter(Procedure.Block.!= "TutorialProc" & Procedure.Block.!= "PracticeProc" & Procedure.Block.!= "BreakProc") #filter to remove tutorial, practice, break rows
```

## Clean up block vars for analyses
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
#Make a combined verison that breaks up acq and reversal across runs
df_bothV <- df_bothV %>% 
  mutate(blockC = coalesce(Acq100Blk.Cycle, ReversalBlk.Cycle))

#This is prob going to be a non-concise way of doing this, but to be extra careful that my blocks align with how I set up physio triggers, I'm doing this the long way by recoding each block chunked by acq and rev in each run

df_bothV <- df_bothV %>% 
  mutate(blockOrder = case_when(
             between(Acq100Blk.Sample, 1,12) ~ 1,
             between(Acq100Blk.Sample, 3,24) ~ 2,
             between(Acq100Blk.Sample, 25,36) ~ 3,
            between(Acq100Blk.Sample, 37,48) ~ 4, 
            between(Acq100Blk.Sample, 49,60) ~ 5, 
            between(Acq100Blk.Sample, 61,72) ~ 6 ,
            between(Acq100Blk.Sample, 73,84) ~ 7, 
            between(Acq100Blk.Sample, 85,96) ~ 8, 
            between(ReversalBlk.Sample, 1,12) ~ 9, 
            between(ReversalBlk.Sample, 13,24) ~ 10,
            between(ReversalBlk.Sample, 25,36) ~ 11,
            between(ReversalBlk.Sample, 37,48) ~ 12, 
            between(ReversalBlk.Sample, 49,60) ~ 13, 
            between(ReversalBlk.Sample, 61,72) ~ 14, 
            between(ReversalBlk.Sample, 73,84) ~ 15, 
            between(ReversalBlk.Sample, 85,96) ~ 16,
            between(Acq100Blk.Sample, 97,108) ~ 17,
            between(Acq100Blk.Sample, 109,120) ~ 18, 
            between(Acq100Blk.Sample, 121,132) ~ 19,
            between(Acq100Blk.Sample, 133,144) ~ 20, 
            between(Acq100Blk.Sample, 145,156) ~ 21, 
            between(Acq100Blk.Sample, 157,168) ~ 22, 
            between(Acq100Blk.Sample, 169,180) ~ 23, 
            between(Acq100Blk.Sample, 181,192) ~ 24, 
            between(ReversalBlk.Sample, 97,108) ~ 25, 
            between(ReversalBlk.Sample, 109,120) ~ 26, 
            between(ReversalBlk.Sample, 121,132) ~ 27, 
            between(ReversalBlk.Sample, 133,144) ~ 28, 
            between(ReversalBlk.Sample, 145,156) ~ 29, 
            between(ReversalBlk.Sample, 157,168) ~ 30, 
            between(ReversalBlk.Sample, 169,180) ~ 31,
            between(ReversalBlk.Sample, 181,192) ~ 32,
            between(Acq100Blk.Sample, 193,204) ~ 33,
            between(Acq100Blk.Sample, 205,216) ~ 34,
            between(Acq100Blk.Sample, 217,228) ~ 35,
            between(Acq100Blk.Sample, 229,240) ~ 36,
            between(Acq100Blk.Sample, 241,252) ~ 37,
            between(Acq100Blk.Sample, 253,264) ~ 38, 
            between(Acq100Blk.Sample, 265,276) ~ 39,
            between(Acq100Blk.Sample, 277,288) ~ 40, 
            between(ReversalBlk.Sample, 193,204) ~ 41,
            between(ReversalBlk.Sample, 205,216) ~42, 
            between(ReversalBlk.Sample, 217,228) ~ 43,
            between(ReversalBlk.Sample, 229,240) ~ 44,
            between(ReversalBlk.Sample, 241,252) ~ 45,
            between(ReversalBlk.Sample, 253,264) ~ 46, 
            between(ReversalBlk.Sample, 265,276) ~ 47,
            between(ReversalBlk.Sample, 277,288) ~ 48,
            between(Acq100Blk.Sample, 289,300) ~ 49, 
            between(Acq100Blk.Sample, 301,312) ~ 50, 
            between(Acq100Blk.Sample, 313,324) ~ 51, 
            between(Acq100Blk.Sample, 325,336) ~ 52, 
            between(Acq100Blk.Sample, 337,348) ~ 53, 
            between(Acq100Blk.Sample, 349,360) ~ 54, 
            between(Acq100Blk.Sample, 361,372) ~ 55, 
            between(Acq100Blk.Sample, 373,384) ~ 56, 
            between(ReversalBlk.Sample, 289,300) ~ 57, 
            between(ReversalBlk.Sample, 301,312) ~ 58, 
            between(ReversalBlk.Sample, 313,324) ~ 59,
            between(ReversalBlk.Sample, 325,336) ~ 60,
            between(ReversalBlk.Sample, 337,348) ~ 61,
            between(ReversalBlk.Sample, 349,360) ~ 62,
            between(ReversalBlk.Sample, 361,372) ~ 63,
            between(ReversalBlk.Sample, 373,384) ~ 64
           ))

#Create an overall run (1-4) variable
df_bothV <- df_bothV %>% 
  mutate(runOrder = case_when(
    between(blockOrder, 1, 16) ~ 1,
    between(blockOrder, 17, 32) ~ 2,
    between(blockOrder, 33, 48) ~ 3,
    between(blockOrder, 49, 64) ~ 4,
            ))

#Create var denonoting whether acq or rev run
df_bothV <- df_bothV %>% 
  mutate(runType = case_when(
    between(blockOrder, 1, 8) ~ "acqRun1",
    between(blockOrder, 17, 24) ~ "acqRun2",
    between(blockOrder, 33, 40) ~ "acqRun3",
    between(blockOrder, 49, 56) ~ "acqRun4",
    between(blockOrder, 9, 16) ~ "revRun1",
    between(blockOrder, 25, 32) ~ "revRun2",
    between(blockOrder, 41, 48) ~ "revRun3",
    between(blockOrder, 57, 64) ~ "revRun4",
            ))

```

## Add accuracy scores for aim 1a and 1b
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

#Recode the outcome for hBayesDM
df_bothV <- df_bothV %>% 
  mutate(outcome = case_when(Active == 'Hit' ~ 1, 
                        Active == 'Other' ~ 0, 
                        Active == 'FalseAlarm' ~ -1)
  )

#Create variable that collapses accuracy across each block
df_bothV <- df_bothV %>% 
  group_by(Subject, blockOrder) %>% 
  mutate(totalHit = 
           length(which(outcome==1))
           ) 

#Recode choice as 1 and 2 for hBayesDM
df_bothV <- df_bothV %>% 
  mutate(choice = ifelse(Stm.RESP == '{SPACE}', 1, 2)
                            )
           
```

## Make final merged file with only vars I need
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
#Final list of variables I need for analyses and/or descriptives and will include in final data files:
#Subject
#Order
#Acq100Blk.Sample
#ReversalBlk.Sample
#Stim
#Version
#trial_type
#Condition
#Stm.RESP
#Total
#Active
#Outcome
#blockC
#blockOrder
#runOrder
#runType
#totalHit

#Pull these final vars for final analysis dataset
df_bothV <- df_bothV %>% 
  dplyr::select(Subject, Order, Acq100Blk.Sample, ReversalBlk.Sample, Stim, Version, trial_type, Condition, Stm.RESP, choice, Total, Active, outcome, blockC, blockOrder, runOrder, runType, totalHit)

```

## Save out final files -- one in cleaning folder and one in analyses
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
write.csv(df_bothV,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/Eprime merging and cleaning/df_bothV.csv")

write.csv(df_bothV,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/4_DATA ANALYSIS/df_bothV.csv")

df_lines <- df_bothV %>% 
  filter(Version == "LineDrawing") #filtered on stim type

#save out the cleaned lines version
write.csv(df_lines,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/Eprime merging and cleaning/df_lines.csv")

write.csv(df_lines,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/4_DATA ANALYSIS/df_lines.csv")

df_pics <- df_bothV %>% 
  filter(Version == "Ecological") #filtered on stim type

#save out the cleaned pics version
write.csv(df_pics,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/3_DATA MERGING & CLEANING/Eprime merging and cleaning/df_pics.csv")

write.csv(df_pics,"~/Library/CloudStorage/Box-Box/BSL General/Projects/LEAP/4_DATA ANALYSIS/df_pics.csv")
```

## Check descriptives
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

#To do later

```


